### 2020-09-11 paper/coloringBergeGraphs.tex
Save!

  \noindent Output: A maximum cardinality stable set in $G$.
\end{alg}
\begin{algtext}
  Let $v_1, \ldots v_n$ be an ordering of vertices of $G$. We will construct a sequence of induced subgraphs $G = G_0 \supseteq G_1 \supseteq \ldots \supseteq G_n$, so that $G_n$ is a required stable set.

@@

  Return $G_n$.
\end{algtext}

@@

  \noindent Output: A stable set which intersects all the maximum cardinality cliques of $G$.
\end{alg}
\begin{algtext}
  We will create a list $Q_1, \ldots Q_t$ of all maximum cardinality cliques of $G$.

@@

\end{algtext}

@@

  \noindent Output: A coloring of $G$ using $\chi(G)$ colors.
\end{alg}
\begin{algtext}
  If $G$ is equal to its maximum cardinality stable set, color all vertices one color and return.

  Else find $S$ intersecting all maximum cardinality cliques of $G$ (\cref{alg:ssIntersectingCliques}). Color recursively all vertices of $G \setminus S$ with $\chi(G \setminus S) = \omega(G \setminus S) = \omega(G) -1$ colors and all vertices of $S$ with one additional color.
\end{algtext}

>>>>

  \noindent Output: A maximum cardinality stable set in $G$.
\end{alg}
\begin{algtext2}
  Let $v_1, \ldots v_n$ be an ordering of vertices of $G$. We will construct a sequence of induced subgraphs $G = G_0 \supseteq G_1 \supseteq \ldots \supseteq G_n$, so that $G_n$ is a required stable set.

@@

  Return $G_n$.
\end{algtext2}

@@

  \noindent Output: A stable set which intersects all the maximum cardinality cliques of $G$.
\end{alg}
\begin{algtext2}
  We will create a list $Q_1, \ldots Q_t$ of all maximum cardinality cliques of $G$.

@@

\end{algtext2}

@@

  \noindent Output: A coloring of $G$ using $\chi(G)$ colors.
\end{alg}
\begin{algtext2}
  If $G$ is equal to its maximum cardinality stable set, color all vertices one color and return.

  Else find $S$ intersecting all maximum cardinality cliques of $G$ (\cref{alg:ssIntersectingCliques}). Color recursively all vertices of $G \setminus S$ with $\chi(G \setminus S) = \omega(G \setminus S) = \omega(G) -1$ colors and all vertices of $S$ with one additional color.
\end{algtext2}

### 2020-09-11 paper/perfectGraphs.tex
Save!

@@

	\noindent Output: Returns whether $G$ contains a pyramid as an induced subgraph.
\end{alg}
\begin{algtext}

@@

If after examining all choices of $b_1, b_2, b_3, s_1, s_2, s_3$ we find no pyramid, output that $G$ contains no pyramid. Since there are $O(|V(G)|^6)$ such choices and it takes a time of $O(|V(G)|^3)$ to analyze each one, the total time is $O(|V(G)|^9)$.
\end{algtext}

@@

	\noindent Output: Returns whether $G$ contains a configuration of type $T_3$ as an induced subgraph.
\end{alg}
\begin{algtext}

@@

Then, for each choice of $v_4$ that is adjacent to $v_1$ and not to $v_2$ and $v_5$ and has a neighbor in $F$ (call it $v_6$) and a nonneibhbor in $X$, we test whether there is a vertex $v_3$, adjacent to $v_2, v_4, v_5$ and not to $v_1$, with a nonneibhbor in $X$. If there is such a vertex $v_3$, find $P$ -- a path from $v_6$ to $v_5$ with interior in $F'$ and return that $v_1, \ldots v_6, P, X$ is a configuration of type $\T_3$. If we exhaust our search and find none, report that graph does not contain it.
\end{algtext}

@@

	\noindent Output: $O(|V(G)|^5)$ subsets of $V(G)$, such that if $C$ is an amenable hole in $G$, then one of the subsets is a near-cleaner for $C$.
\end{alg}
\begin{algtext}
	We will call a triple $(a, b, c)$ of vertices \emph{relevant} if $a, b$ are distinct (possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.

@@

	Output all subsets of $V(G)$ that are the union of a set from the first list and a set from the second list.
\end{algtext}

@@

	\noindent Output: Determines one of the following:
	\begin{itemize}
		\item $G$ has an odd hole
		\item There is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.
	\end{itemize}
\end{alg}
\begin{algtext}
	For every pair $x, y \in V(G)$ of distinct vertices find shortest path $R(x, y)$ between $x, y$ with no internal vertex in $X$. If there is one, let $r(x, y)$ be its length, if not, let $r(x, y)$ be infinite.

@@

	If there is such a choice of $x_1$, $x_2$, $x_3$, $y_1$ then we output that there is an odd hole. If not, we report that there is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.
\end{algtext}

>>>>

% \begin{algorithm}
% 	\SetKwFunction{ContainsPyramid}{\textsc{Contains-Pyramid}}
% 	% \Indm\nonl\ContainsPyramid{$G$}\\
% 	\KwData{$G = (V, E)$ -- a graph}
% 	\KwResult{Whether $G$ contains a pytamid as an induced subgraph.}
% 	\Indp

% 	\ForEach{ triangle $b_1, b_2, b_3$ }{
% 		\ForEach{ $s_1, s_2, s_3$, such that for $1 \leq i < j \leq 3$, $\{b_i, s_i\}$ is disjoint from $\{b_j, s_j\}$ and $b_ib_j$ is the only edge between them }{
% 			\If{ there is a vertex $a$, adjacent to all of $s_1, s_2, s_3$, and to at most one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $b_i = s_i$ } {
% 				$M \gets V(G) \setminus \{b_1, b_2, b_3, s_1, s_2, s_3\}$\;
% 				\ForEach{$m \in M$} {
% 					$S_1(m) \gets$ the shortest path between $s_1$ and $m$ such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists. \;
% 					Calculate $S_2(m), S_3(m)$ similarly\;
% 					$T_1(m) \gets$ the shortest path between $m$ and $b_1$, such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists\;
% 					Calculate $T_2(m), T_3(m)$ similarly\;
% 				}
% 				\ForEach{$m \in M \cup \{b_1\}$}{
% 					\If{$s_1 = b_1$}{
% 						$P_1(b_1) \gets$ the one-vertex path with vertex $b_1$\;
% 						$\forall_{m \in M}: P_1(m) \gets$ \textsc{undefined}\;
% 					} \Else{
% 						$P_1(b_1) \gets $ \textsc{undefined}\;
% 						\ForEach{$m \in M$}{
% 							\If{all the following are true:
% 								\begin{itemize}
% 									\item $m$ is nonadjacent to all of $b_2, b_3, s_2, s_3$
% 									\item $S_1(m)$ and $T_1(m)$ both exist
% 									\item $V(S_1(m) \cap T_1(m)) = \{m\}$
% 									\item there are no edges between $V(S_1(m) \setminus m)$ and $V(T_1(m) \setminus m)$
% 								\end{itemize}
% 							}
% 							{
% 								TODO\;
% 							}
% 						}
% 					}
% 				}
% 			}
% 		}
% 	}

% 	\label{aab}
% 	\caption{Contains-Pyramid}
% \end{algorithm}

@@

	\noindent Output: Returns whether $G$ contains a pyramid as an induced subgraph.
\end{alg}
\begin{algtext2}

@@

	If after examining all choices of $b_1, b_2, b_3, s_1, s_2, s_3$ we find no pyramid, output that $G$ contains no pyramid. Since there are $O(|V(G)|^6)$ such choices and it takes a time of $O(|V(G)|^3)$ to analyze each one, the total time is $O(|V(G)|^9)$.
\end{algtext2}

@@

	\noindent Output: Returns whether $G$ contains a configuration of type $T_3$ as an induced subgraph.
\end{alg}
\begin{algtext2}

@@

	Then, for each choice of $v_4$ that is adjacent to $v_1$ and not to $v_2$ and $v_5$ and has a neighbor in $F$ (call it $v_6$) and a nonneibhbor in $X$, we test whether there is a vertex $v_3$, adjacent to $v_2, v_4, v_5$ and not to $v_1$, with a nonneibhbor in $X$. If there is such a vertex $v_3$, find $P$ -- a path from $v_6$ to $v_5$ with interior in $F'$ and return that $v_1, \ldots v_6, P, X$ is a configuration of type $\T_3$. If we exhaust our search and find none, report that graph does not contain it.
\end{algtext2}

@@

	\noindent Output: $O(|V(G)|^5)$ subsets of $V(G)$, such that if $C$ is an amenable hole in $G$, then one of the subsets is a near-cleaner for $C$.
\end{alg}
\begin{algtext2}
	We will call a triple $(a, b, c)$ of vertices \emph{relevant} if $a, b$ are distinct (possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.

@@

	Output all subsets of $V(G)$ that are the union of a set from the first list and a set from the second list.
\end{algtext2}

@@

	\noindent Output: Determines one of the following:
	\begin{itemize}
		\item $G$ has an odd hole
		\item There is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.
	\end{itemize}
\end{alg}
\begin{algtext2}
	For every pair $x, y \in V(G)$ of distinct vertices find shortest path $R(x, y)$ between $x, y$ with no internal vertex in $X$. If there is one, let $r(x, y)$ be its length, if not, let $r(x, y)$ be infinite.

@@

	If there is such a choice of $x_1$, $x_2$, $x_3$, $y_1$ then we output that there is an odd hole. If not, we report that there is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.
\end{algtext2}
